{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex
correction
Small correction

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. As it can be seen, the measurmant points can be differentiated through each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$. In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable. The several basis systems to make the functional data smooth is introduced from the next sub-chapter.\\
	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis. The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible. An example of such a data set could be the data set of 60 N

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^k \quad i \in \mathcal{I}
	\end{equation}
	The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
	The shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
	 There exists problems of collinearity of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. Therefore, regarding the use, this may be useful for relatively simple functions. However, the small number of degrees makes it impossible to capture pronounced local peculiarities {\color{orange} (Isn't it good as thinking of the Taylor? The use of MB for local expansion? Need to check.)} and leads to undesirable behavior at the tails such as Taylor expansion. (cf. \cite{ramsay_functional_2005})

>>>>

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^k \quad i \in \mathcal{I}
	\end{equation}
	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation. The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. Therefore, regarding the use, this may be useful for relatively simple functions. However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities. Moreover, it leads to an undesirable behavior at the tails such as Taylor expansion. (cf. \cite{ramsay_functional_2005})
